Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-12-07 paper/paper.tex
replace $G(z)$ by $\hat{G}(z)$ in proposition 1, item 2
Updated experiment table with both back-ends.

\begin{myprop}{\cite{fadali,Bessa16}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\hat{C}(z) =\mathit{FWL}_{M_C,N_C}[C(z)]$ and uncertain discrete
model of the plant
%
$$\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
\vec{G} \text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=\mathit{FWL}_{M_C}[C_n(z)]\hat{G}_n(z)+\mathit{FWL}_{N_C}[C_d(z)]\hat{G}_d(z);
\end{equation}
\item the direct loop product $\mathit{FWL}_{M_C,N_C}[C(z)]\cdot G(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{myprop}

@@

\begin{table}
\centering
\begin{tabular}{c | c | l | r r | r l}
\# & Plant  & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-6}
1  & $G_1$  & CruiseControl02            &   4 &  16 & 17\,s   & \\
2  & $G_1$  & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
3  & $G_2$  & SpringMassDamper           &  15 &  16 & 28\,s   & \\
4  & $G_2$  & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
5  & $G_3$  & SatelliteB2                &   3 &   7 & 7\,s    & \\
6  & $G_3$  & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
7  & $G_3$  & SatelliteC2                &   3 &   5 & 2\,s    & \\
8  & $G_3$  & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
9  & $G_4a$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
10 & $G_4a$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
11 & $G_4a$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
12 & $G_4b$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
13 & $G_4b$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
14 & $G_4b$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
15 & $G_4c$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with the one-stage engine, $\dagger$ = with uncertainty}
\vspace{0.5em}

>>>>

\begin{myprop}{\cite{fadali,Bessa16}}
\label{prop:eq_int_stab} 
%
Consider a feedback closed-loop control system as given in
Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
controller $\hat{C}(z) =\mathit{FWL}_{M_C,N_C}[C(z)]$ and uncertain discrete
model of the plant
%
$$\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
\vec{G} \text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}$$
%
Then $\hat{G}(z)$ is BIBO-stable if and only if:
%
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=\mathit{FWL}_{M_C}[C_n(z)]\hat{G}_n(z)+\mathit{FWL}_{N_C}[C_d(z)]\hat{G}_d(z);
\end{equation}
\item the direct loop product $\mathit{FWL}_{M_C,N_C}[C(z)]\cdot \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{myprop}

@@

\begin{table}
\centering
\begin{tabular}{ | c | c | l | r r || r | r | }
\hline
\# & Plant  & Benchmark                  & $I$ & $F$
   & \multicolumn{1}{|c|}{1-step} & \multicolumn{1}{|c|}{2-step}
    \\\hline\hline
1  & $G_1$  & CrsControl02
            &   4 &  16 & 17\,s   & \xmark     \\
2  & $G_1$  & CrsControl02$^\dagger$
            &   4 &  16 & 46\,s   & \xmark     \\
3  & $G_2$  & SpgMsDamper
            &  15 &  16 & 28\,s   & \xmark     \\
4  & $G_2$  & SpgMsDamper$^\dagger$
            &  15 &  16 & \xmark  & \xmark    \\
5  & $G_3$  & SatelliteB2
            &   3 &   7 & 7\,s    & \xmark     \\
6  & $G_3$  & SatelliteB2$^\dagger$
            &   3 &   7 & \xmark  & 6601\,s  \\
7  & $G_3$  & SatelliteC2
            &   3 &   5 & 2\,s    & \xmark    \\
8  & $G_3$  & SatelliteC2$^\dagger$
            &   3 &   5 & \xmark  & 76\,s    \\
9  & $G_4a$ & a\_ST1\_IMPL1
            &  16 &   4 & 2704\,s & \xmark   \\
10 & $G_4a$ & a\_ST1\_IMPL2
            &  16 &   8 & 538\,s  & \xmark   \\
11 & $G_4a$ & a\_ST1\_IMPL3
            &  16 &  12 & 12\,s   & \xmark   \\
12 & $G_4b$ & a\_ST2\_IMPL1
            &  16 &   4 & 318\,s  & \xmark   \\
13 & $G_4b$ & a\_ST2\_IMPL2
            &  16 &   8 & 967\,s  & \xmark    \\
14 & $G_4b$ & a\_ST2\_IMPL3
            &  16 &  12 & 9798\,s & \xmark   \\ 
15 & $G_4c$ & a\_ST3\_IMPL1
            &  16 &   4 & 6304\,s & \xmark   \\\hline
\end{tabular}

\vspace{0.5em}
\scriptsize{\xmark = time-out, $\dagger$ = with uncertainty}
\vspace{0.5em}
